An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd
merge and add plots generated from data files

\wj{the followings are revised} \hh{XXX this section feels a bit repetitive}
* `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
* `seg_length` specifies the length of basis segments [(in mm?)] mentioned in algorithm step 1; 
* `Tx` determines the size of the tolerance zone mentioned in both step 2 and 3;
* `npeaks.set` is a (vector of) integer value(s). This parameter determines which strategy to use to generate candidate positions and the number of peaks to be identified;
* `include` determines the output of the function. Besides the `CMPS.score`, many details of the comparison might be used to understand how the `CMPS.score` is computed. By default, `include = NULL` and the function output will only contain the `CMPS.score`; `include` can also be (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`. if `"full_result"` (or its abbreviation) is specified, the ouput will include everything listed below.
  - `nseg`: the number of basis segments we get from the reference signature; this is also the highest possible CMPS score of the comparison;
  - `congruent.pos`: the congruent registration position;
  - `congruent.seg.idx`: the indices of all congruent matching profile segments;
  - `ccp.list`: a list showing identified candidate positions of all basis segments; 
  - `pos.df`: a data frame containing all candidate positions and the number of votes they received;
  - `segments`: a list containing all basis segments;
  - `parameters`: a list containing all input arguments of `extract_feature_cmps`;

@@

The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively. This comparison is one of the KM comparisons. We compute the CMPS score using two versions of the CMPS algorithm:

one of a pair of signatures that are known to be a match -- a KM (known match) comparison

@@

>>>>

\wj{the followings are revised} \hh{XXX this section feels a bit repetitive}

* `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
* `seg_length` specifies the length of basis segments [(in mm?)] mentioned in algorithm step 1; 
* `Tx` determines the size of the tolerance zone mentioned in both step 2 and 3;
* `npeaks.set` is a (vector of) integer value(s). This parameter determines which strategy to use to generate candidate positions and the number of peaks to be identified;
* `include` determines the output of the function. Besides the `CMPS.score`, many details of the comparison might be used to understand how the `CMPS.score` is computed. By default, `include = NULL` and the function output will only contain the `CMPS.score`; `include` can also be (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`. if `"full_result"` (or its abbreviation) is specified, the ouput will include everything listed below.
  - `nseg`: the number of basis segments we get from the reference signature; this is also the highest possible CMPS score of the comparison;
  - `congruent.pos`: the congruent registration position;
  - `congruent.seg.idx`: the indices of all congruent matching profile segments;
  - `ccp.list`: a list showing identified candidate positions of all basis segments; 
  - `pos.df`: a data frame containing all candidate positions and the number of votes they received;
  - `segments`: a list containing all basis segments;
  - `parameters`: a list containing all input arguments of `extract_feature_cmps`;

@@

The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively. This comparison is one of a pair of signatures that are known to be a match -- a KM (known match) comparison. We compute the CMPS score using two versions of the CMPS algorithm:

@@

```{r, eval=TRUE, echo=TRUE, fig.height=3}
CMPS_hamby252_results$plot[[1]]
```
